---
title: "Project proposal"
author: "Team 404"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
```

## 1. Introduction

We are going to work with the "Friends" data package from TidyTuesday.
It was aggregated, packaged, and shared by Emil Hvitfeldt.

We will try to look behind the levels of popularity throughout all 10 seasons, and ask the ultimate question:

What makes the perfect "Friends" episode?

The package consists of 4 data sets: 
friends : transcript of all dialogues containing information on the speaker, episode, season, scene, utterance
friends_emotions : information on the emotions of each utterance with specified scene, episode, and season number
friends_entities : character entities with info on utterance, scene, episode, season
friends_info : here we have information on each episode: title, episode number, season number, name of writer and director, airing date, number of views and IMDB ratings.






## 2. Data
```{r load-packages, message = FALSE}
glimpse(friends)
glimpse(friends_emotions)
glimpse(friends_info)
```
## 3. Data analysis plan



