---
title: "Project proposal"
author: "Team 404"
output: github_document
---

```{r load-packages, message = FALSE, echo = FALSE}
library(tidyverse)
library(broom)
library(friends)
```

## 1. Introduction

We are going to work with the "Friends" data package from TidyTuesday.
It was aggregated, packaged, and shared by Emil Hvitfeldt.
We load it from the `friends` R package.

We will try to look behind the levels of popularity throughout all 10 seasons, and ask the ultimate question:

What makes the perfect "Friends" episode?

The package consists of 4 data sets: 

friends : consists of 67,373 rows and 6 columns. It is a transcript of all dialogues where each row represents an utterance. The variables contain information on `text`, the `speaker`, `episode`, `season`, `scene`, and the number of utterance - `utterance`;

friends_emotions : consists of 12,606 rows and 5 columns. Each row representing an utterance, variables give information on the number of each `utterance` and its `emotion`, with specified `scene`, `episode`, and `season` number;

friends_entities : consists of 10.557 rows and 5 columns. Each row being one utterance, variables show detail on utterance number - `utterance`, `entity`, `scene`, `episode`, `season`;

friends_info : consists of 236 rows and 8 columns. Each row represents an episode. Variables are: title, episode number, season number, name of writer and director, airing date, number of views and IMDB ratings.



## 2. Data
```{r glimpse-data, echo = FALSE}
glimpse(friends)
glimpse(friends_emotions)
glimpse(friends_info)
```
## 3. Data analysis plan

We will explore this question through a number of visualizations. We are using the word 'Perfect' to mean the episode which generates the highest audience satisfaction and so we will use the IMDB rating (`imdb_rating`) of each episode as the response variable to evaluate the impact of each factor on the quality of the episode. We decided against using the view count, as the number of views of an episode does not necessarilly reflect how it was recieved.

The factors which we will explore include: the  characters (`speaker`) which appear with the most prominence, the tone (`emotion`), the writer(`written_by`), and the director (`directed_by`) of each episode. We can also see which variable has the largest impact on viewer satisfaction in this way.

```{r data-reconstruct, echo = FALSE}
friendsWanted <- friends %>%
  filter( 
    speaker == "Joey Tribbiani"|
    speaker == "Chandler Bing"|
    speaker == "Monica Geller"|
    speaker == "Phoebe Buffay"|
    speaker == "Rachel Green"|
    speaker == "Ross Geller"
  ) %>% 
  group_by(season, episode) %>% 
  count(speaker) %>%
  merge(friends_info, by=c("episode","season"))

```

```{r character-vs-rating, echo = FALSE}
friendsWanted %>% 
  ggplot(aes( x = n, y = imdb_rating, color = speaker))+
  geom_point()+
  geom_smooth(color = "black")+
  facet_wrap('.~speaker')+
  labs( title = "Episode Ratings vs How much each character spoke",
        x = "Number of Lines",
        y = "IMBD Rating",
        color = "Character"
      )+
  scale_color_viridis_d()
```

This visualization enables us to see how the Number of lines spoken by each character influences the IMDB rating for that episode. Using just a scatter plot it is difficult to see a connection between the variables, so a trend line was used to reveal a connection. However, the trend line seems to be largely influenced by extreme values, so we will need to do more analysis to see if these values are outliers which need to be removed.

```{r rating_per_writer, echo = FALSE}
friendsWanted %>% 
  group_by(written_by) %>% 
  summarise(mean_rating = mean(imdb_rating), med_rating = median(imdb_rating)) %>% 
  arrange(desc(mean_rating))
```
 In this summary statistic you can see which writers achieved the highest mean IMDB rating. It also becomes clear that the 'written_by' variable does not only contain singular names. We many need to alter this data again to provide only singular names in the 'written_by' variable in order to see more clearly which writers are preferred. 
 
Furthermore, some of the observations show that some writers have the same median and mean rating, leading us to the think that there may only be one episode represented. The sample size of these writers' episodes may thus be too small to draw any meaning full conclusions

```{r writer_episode_count, echo = FALSE}
friendsWanted %>% 
  count(written_by) %>%
  arrange(n)
```
In this table we can see the how many episodes each 'writer' has written, and by arranging them in ascending order we can see that the minimum number of episodes is 6. We must explore as to whether this is an adequate sample size




