---
title: "The Perfect Friends Episode"
#subtitle: "Presentation subtitle (if any)"
author: "Team 404: Sophie Bata-Madden, Natalia Okanikova, Barney Gray"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
editor_options: 
  chunk_output_type: console
---


```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(friends)
library(xaringanthemer)
library(showtext)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Load your data here
# Our data is loaded with the 'friends' package
```


```{r xaringan-themer, include = FALSE, message=FALSE}
style_duo_accent(
  primary_color = "#b0e2ff",
  secondary_color = "#ffa8a3",
  background_color = "#fff7c4"
  )
```


class: center, middle

# What makes the perfect "Friends" episode?

---

class: inverse, middle, center

# Which Factors influence IMBD Rating?

---

# Characters

```{r data-reconstruct, echo = FALSE}
friends_wanted <- friends %>%
  filter( 
    speaker == "Joey Tribbiani"|
    speaker == "Chandler Bing"|
    speaker == "Monica Geller"|
    speaker == "Phoebe Buffay"|
    speaker == "Rachel Green"|
    speaker == "Ross Geller"
  ) %>% 
  group_by(season, episode) %>% 
  count(speaker) %>%
  merge(friends_info, by=c("episode","season"))
```

```{r pivot-wider-for-speaker-model, include=FALSE}
friends_wanted_wider <- friends_wanted %>%
  pivot_wider(names_from = speaker, values_from = n) %>%
  arrange(season, episode)
```

```{r friends-speaker-lr, echo = FALSE}

friends_speaker_lr <- linear_reg() %>%
  set_engine("lm") %>%
  fit(imdb_rating ~ `Chandler Bing` + `Rachel Green` + `Ross Geller` + `Phoebe Buffay` + 
        `Joey Tribbiani` + `Monica Geller`, data = friends_wanted_wider)

tidy(friends_speaker_lr)

glance(friends_speaker_lr)
```

---
# Characters

```{r character-vs-rating, echo = FALSE, message = FALSE}
friends_wanted %>% 
  ggplot(aes( x = n, y = imdb_rating, color = speaker))+
  geom_point()+
  geom_smooth(method = "lm",
              se = FALSE, 
              color="black")+
  facet_wrap('.~speaker')+
  labs( title = "Episode Ratings vs How much each character spoke",
        x = "Number of Lines",
        y = "IMDB Rating"
      )+
  scale_color_manual(values = c("#ff4238", "#007ade", "#9a000b", "#00009e", 
                                "#ff736b", "#42a2db")) +
  theme(legend.position = "none",
        plot.background = element_rect(fill = "#fff7c4") )
```
<<<<<<< HEAD
=======
--
>>>>>>> 7e31d7cfded4d4c3fb5126a99dee793285db7781

This plot shows us that Ross and Monica have the highest impact in terms of when they have more lines the IMDB rating of the show on average increases more than when the other characters do. It seems though that as every characters number of lines increases the rating does so too slightly. 

---
# Tone
```{r prepare-data-for-tone-model, include = FALSE}
friends_emotions_wider <- friends_emotions %>%
  group_by(season,episode,emotion) %>%
  count()%>%
  pivot_wider(names_from = emotion, values_from = n)
```
```{r join-imdb, include=FALSE}
friends_emotions_wider <- friends_emotions_wider %>%
  left_join(friends_wanted_wider, season = season, episode = episode) %>%
  select(- `Chandler Bing`, - `Rachel Green`, - `Ross Geller`, - `Monica Geller`, - `Joey Tribbiani`, -`Phoebe Buffay`, -`air_date`, -`us_views_millions`, -`written_by`, -`directed_by` )
```

```{r friends-tone-lr, echo = FALSE}
friends_tone_lr <- linear_reg() %>%
  set_engine("lm") %>%
  fit(imdb_rating ~ Joyful +  Mad + Neutral + Peaceful + Powerful + Sad + Scared, data = friends_emotions_wider)

tidy(friends_tone_lr)

glance(friends_tone_lr)
```

Note: we only have info on first 4 seasons

---
# Tone
```{r tone-vs-imdb-rating, echo = FALSE, message = FALSE}
friends_emotions %>% 
  group_by(season, episode) %>% 
  count(emotion) %>%
  merge(friends_info, by=c("episode","season")) %>% 
  ggplot(aes( x = n, y = imdb_rating, color = emotion))+
  geom_point()+
  geom_smooth(method = "lm",
              se = FALSE, 
              color="black")+
  facet_wrap('.~emotion')+
  labs( title = "Episode Ratings vs How many utterances of a certain tone",
        x = "Number of Utterances",
        y = "IMDB Rating"
      )+
  scale_color_manual(values = c("#a8d8ff", "#ff4238", "#007ade", "#9a000b", "#00009e", 
                                "#ff817a", "#42a2db")) +
  theme(legend.position = "none",
        plot.background = element_rect(fill = "#fff7c4")) 

```

Note: we only have info on first 4 seasons

-- 

This plot suggests that as the number of utterances of peaceful, powerful and scared tone increase as does the average rating. However, episodes that have a more mad or sad tone decrease in rating.

---

#Writer

Here we look at the top 10 writers with 10 or more episodes.
```{r writers-split, echo = FALSE}
writers <- friends_info %>%
  mutate(written_by = str_remove(written_by, "Story by :")) %>% 
  mutate(written_by = str_replace(written_by,"Teleplay by :", "\\&"))


writers <- writers %>% 
  mutate(written_by = strsplit(as.character(written_by), "\\&")) %>% 
  unnest(written_by) %>% 
  mutate(written_by = str_squish(written_by))
```

```{r writer-avg-imdb-rating, echo = FALSE, message = FALSE}
writers_sum <- writers %>% 
  group_by(written_by) %>% 
  summarise(mean_rating = mean(imdb_rating), med_rating = median(imdb_rating), n_episodes = n()) %>% 
  arrange(desc(mean_rating))
```
```{r writer-avg-over10, echo = FALSE, message = FALSE}
writers_sum2 <- writers_sum %>% 
 filter(n_episodes > 9)

kable(head(writers_sum2, n = 10), format = "html")

```
--
This shows that according to mean and median rating, David Crane is the most popular writer for the show of those who wrote more than 10. Seeing as shows are often co-written it is fair to also note that the 'ideal' episode may be written by both Marta Kauffman and David Crane. 
---
#Director

```{r dir-avg-imdb-rating, echo = FALSE, message = FALSE}
dir_sum <- friends_info %>% 
  group_by(directed_by) %>% 
  summarise(mean_rating = mean(imdb_rating), med_rating = median(imdb_rating), n_episodes = n()) %>% 
  arrange(desc(mean_rating)) %>% 
  filter(n_episodes > 9)

kable(head(dir_sum, n = 10), format = "html")
```

Kevin S. Bright has the highest mean and median rating cementing him as the top director. He also directed many more episodes than most other directors at 53.
---
# Season

```{r imdb-rating-over-time, echo = FALSE, message = FALSE}
friends_info$season_episode <- paste(friends_info$season, friends_info$episode)

friends_info %>%
  mutate(season_episode = str_replace(season_episode, " ", "\\.")) %>%
  ggplot(aes(x = season_episode, y = imdb_rating)) +
  geom_point(stat = "identity") +
  labs(title = "IMDB Rating per Episode", x = "Season/Episode", y = "IMDB Rating") +
  theme(axis.text.x = element_text(angle=45),  plot.background = element_rect(fill = "#fff7c4")) +
  scale_x_discrete(breaks = c(1.1, 2.1, 3.1, 4.1, 5.1, 6.1, 7.1, 8.1, 9.1, 10.1))

```

---
# Outcome

According to our models, the perfect "Friends" episode should be:
 - written by David Crane (or Suzie Villandry)
 - directed by Kevin S. Bright (or David Schwimmer)
 - scared and peaceful 
 - mostly the Gellers talking 
 
```{r predicted-best-episode, echo = FALSE}
#writers %>%
#  left_join (friends_wanted_wider, season = season, episode = episode)%>%
 # filter(written_by == "David Crane" | written_by == "Suzie Villandry",
 #        directed_by== "Kevin S. Bright" | directed_by == "David Schwimmer")%>%
```

---
# Outcome

the actual "perfect" episode is:

```{r}
friends_info_arranged <- friends_info %>%
  arrange(desc(imdb_rating))%>%
  select(season, episode, title, imdb_rating, written_by, directed_by)

kable(head(friends_info_arranged, n = 10))
```
 I haven't added how much each character speaks yet but will do 

