---
title: "The Perfect Friends Episode"
#subtitle: "Presentation subtitle (if any)"
author: "Team 404: Sophie Bata-Madden, Natalia Okanikova, Barney Gray"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(friends)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Load your data here
# Our data is loaded with the 'friends' package
```


class: center, middle

What makes the perfect "Friends" episode?

---

class: inverse, middle, center

# Which Factors influence IMBD Rating?

---

# Characters

```{r data-reconstruct, echo = FALSE}
friends_wanted <- friends %>%
  filter( 
    speaker == "Joey Tribbiani"|
    speaker == "Chandler Bing"|
    speaker == "Monica Geller"|
    speaker == "Phoebe Buffay"|
    speaker == "Rachel Green"|
    speaker == "Ross Geller"
  ) %>% 
  group_by(season, episode) %>% 
  count(speaker) %>%
  merge(friends_info, by=c("episode","season"))
```
We should prob do something with regression here before we show the plot? -- i'm trying to 
find the slope for each speaker and its not working
```{r friends-speaker-lr}
#friends_wanted_l <- linear_reg() %>%
#  set_engine("lm") %>%
#  fit(imdb_rating ~ n, data = friends_wanted)
friends_wanted_lr <- friends_wanted %>% 
  group_by(speaker) %>% 
  nest() %>% 
  mutate(model = map(data, ~lm(imdb_rating ~ n, data = friends_wanted))) #) %>% 
 # unnest()



```

---

```{r character-vs-rating, echo = FALSE, message = FALSE}
friends_wanted %>% 
  ggplot(aes( x = n, y = imdb_rating, color = speaker))+
  geom_point()+
  geom_smooth(method = "lm",
              se = FALSE, 
              color="black")+
  facet_wrap('.~speaker')+
  labs( title = "Episode Ratings vs How much each character spoke",
        x = "Number of Lines",
        y = "IMDB Rating"
      )+
  scale_color_viridis_d()+
  theme(legend.position = "none") 
```
--

- Insert Short Summary of visualisation 

---
# Tone

```{r tone-vs-imdb-rating, echo = FALSE, message = FALSE}
friends_emotions %>% 
  group_by(season, episode) %>% 
  count(emotion) %>%
  merge(friends_info, by=c("episode","season")) %>% 
  ggplot(aes( x = n, y = imdb_rating, color = emotion))+
  geom_point()+
  geom_smooth(method = "lm",
              se = FALSE, 
              color="black")+
  facet_wrap('.~emotion')+
  labs( title = "Episode Ratings vs How many utterances of a certain tone",
        x = "Number of Utterances",
        y = "IMDB Rating"
      )+
  scale_color_viridis_d()+
  theme(legend.position = "none") 

```
---
# Writer

```{r writer-cleanse, echo = FALSE}
writers <- friends_info %>%
  mutate(written_by = str_remove(written_by, "Story by :")) %>% 
  mutate(written_by = str_replace(written_by,"Teleplay by :", "\\&"))

view(writers)

```

```{r writers-split, echo = FALSE}
writers <- writers %>% 
  mutate(written_by = strsplit(as.character(written_by), "\\&")) %>% 
  unnest(written_by) %>% 
  mutate(written_by = str_squish(written_by))
```

```{r writer-avg-imdb-rating, message = FALSE}
writers %>% 
  group_by(written_by) %>% 
  summarise(mean_rating = mean(imdb_rating), med_rating = median(imdb_rating), n_episodes = n()) %>% 
  arrange(desc(mean_rating))
```

Should we consider writers with not many episodes?

---
#Writer (cont.)

Here we look at writers with 10 or more episodes.

```{r writer-avg-over10, echo = FALSE, message = FALSE}
writers %>% 
  group_by(written_by) %>% 
  summarise(mean_rating = mean(imdb_rating), med_rating = median(imdb_rating), n_episodes = n()) %>%
  filter(n_episodes > 9) %>% 
  arrange(desc(mean_rating))
```

---
# Layouts

You can use plain text

- or bullet points

.pull-left[
or text in two columns $^*$
]
.pull-right[
- like
- this
]

.footnote[
[*] And add footnotes
]

---

# Code

```{r boring-regression}
# a boring regression
model <- lm(dist ~ speed, data = cars)
tidy(model)
glance(model)
```

---

# Plots

```{r recode-species, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
iris_modified <- iris %>%
  mutate(Species = fct_other(Species, keep = "setosa"))
```

```{r plot-iris, echo = FALSE}
# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the look
ggplot(data = iris_modified, mapping = aes(x = Sepal.Width, y = Sepal.Length, color = Species)) +
  geom_point() + 
  theme_minimal() # theme options: https://ggplot2.tidyverse.org/reference/ggtheme.html
```

---

## Plot and text

.pull-left[
- Some text
- goes here
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
]

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(iris), format = "html")
```

---

# Images

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

Or you can also include a full page image. See next slide.

---

background-image: url(https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80)

---

# Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;

1. There should not be spaces after the opening `$` or before the closing `$`.

1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---

# Feeling adventurous?

- Want to find out more about `xaringan`? See https://slides.yihui.name/xaringan/#1.

- You are welcomed to use the default styling of the slides. In fact, that's what I expect majority of you will do. You will differentiate yourself with the content of your presentation.

- But some of you might want to play around with slide styling. The 
`xaringanthemer` provides some solutions for this that: https://pkg.garrickadenbuie.com/xaringanthemer.

- And if you want more bells and whistles, there is also `xaringanExtra`: https://pkg.garrickadenbuie.com/xaringanExtra.
